Enforced Invariant Confluence

### 2018-03-29 doc/paper/sections/introduction.tex
Part of iclosure, part of intro, title ideas.

\section{Introduction}
% Hype up problem that invariant confluence solves
% Introduce iconfluence and hype it up as a really good thing.
% Discuss how it's hard to determine iconfluence and a lot of existing
% approaches fall short.
% Describe how we take the problem one step further
% Overview two new approaches
% Describe how often times we're not iconfluent
% Overivew new segmented iconfluence stuff
% contributions
%   - new expression-based definitions of iconfluence
%   - understanding of iclosure and new suff and necc
%   - interactive decision procedure
%   - new suff conditions
%   - segmented iconfluence
%   - implementation in lucy + evaluation...

>>>>

\section{Introduction}
In summary, our contributions are as follows:
\begin{itemize}
  \item
    We propose a novel expression-oriented definition of invariant-confluence
    that is both formal and simple (\secref{InvariantConfluence}).

  \item
    We develop conditions under which invariant-closure is both necessary and
    sufficient for invariant-confluence (\secref{InvariantClosure}).

  \item
    We exploit these conditions to design an interactive decision procedure for
    invariant-confluence (\secref{InteractiveDecisionProcedure}).

  \item
    We again exploit these conditions to design a novel non-trivial sufficient
    condition for invariant-confluence that does not depend on user interaction
    (\secref{???}).

  \item
    We present segmented invariant-confluence: a generalization of
    invariant-confluence that uses a small amount of coordination to maintain
    invariants for replicated objects that are otherwise not
    invariant-confluent (\secref{SegmentedInvariantConfluence}).

  \item
    We implement and evaluate our theoretical findings in a system called Lucy
    (\secref{Evaluation}).
\end{itemize}

% Hype up problem that invariant confluence solves
% Introduce iconfluence and hype it up as a really good thing.
% Discuss how it's hard to determine iconfluence and a lot of existing
% approaches fall short.
% Describe how we take the problem one step further
% Overview two new approaches
% Describe how often times we're not iconfluent
% Overivew new segmented iconfluence stuff
% contributions
%   - new expression-based definitions of iconfluence
%   - understanding of iclosure and new suff and necc
%   - interactive decision procedure
%   - new suff conditions
%   - segmented iconfluence
%   - implementation in lucy + evaluation...

### 2018-03-29 doc/paper/sections/invariant_closure.tex
Part of iclosure, part of intro, title ideas.

\section{Invariant-Closure}
% - define invariant-closure and introduce it as a sufficient condition
% - cite existing work to show that people have used invariant closure to
%   reason about invariant-confluence
% - explain why invariant closure can fail and why its not sufficient using the
%   two-integers example
% - state main theorem

>>>>

\section{Invariant-Closure}\seclabel{InvariantClosure}
Our ultimate goal is to write a program that can automatically decide whether a
given distributed object $O$ is \sTIconfluent{}. Such a program has to
automatically prove or disprove that every reachable state satisfies the
invariant. However, automatically reasoning about the possibly infinite set of
reachable states is challenging, especially because transactions and merge
functions can be complex and can be interleaved arbitrarily in an execution.
Due to this complexity, existing systems that aim to automatically decide
invariant-confluence instead focus on deciding a sufficient condition for
invariant-confluence---dubbed \defword{invariant-closure}---that is simpler to
reason about~\cite{li2012making, li2014automating}. In this section, we define
invariant-closure and study why the sufficient condition is not necessary.
Armed with this understanding, we present conditions under which it is both
sufficient and necessary.

% - define invariant-closure and introduce it as a sufficient condition
% - cite existing work to show that people have used invariant closure to
%   reason about invariant-confluence
% - explain why invariant closure can fail and why its not sufficient using the
%   two-integers example
% - state main theorem

### 2018-03-29 doc/paper/sections/invariant_confluence.tex
Part of iclosure, part of intro, title ideas.

\section{Invariant-Confluence}
Informally, a replicated object is \defword{invariant-confluent} with respect
to an invariant if every replica of the object is guaranteed to satisfy the
invariant despite the possibility of different replicas being concurrently
modified or merged together~\cite{bailis2014coordination}. In this section, we
make this informal notion of invariant-confluence precise. We begin by
introducing our system model of replicated objects and then present a formal
definition of invariant-confluence.

@@

Finally, we say $O$ is \defword{invariant-confluent with respect to $s_0$, $T$,
and $I$}, abbreviated \defword{\sTIconfluent{}}, if all reachable states
satisfy the invariant: $\setst{s \in S}{\sTIreachable{s}} \subseteq I$.

>>>>

\section{Invariant-Confluence}\seclabel{InvariantConfluence}
Informally, a replicated object is \defword{invariant-confluent} with respect
to an invariant if every replica of the object is guaranteed to satisfy the
invariant despite the possibility of different replicas being concurrently
modified or merged together~\cite{bailis2014coordination}. In this section, we
make this informal notion of invariant-confluence precise. We begin by
introducing our system model of replicated objects and then present a formal
definition of invariant-confluence.

@@

Finally, we say $O$ is \defword{invariant-confluent with respect to $s_0$, $T$,
and $I$}, abbreviated \defword{\sTIconfluent{}}, if all reachable states
satisfy the invariant: $\setst{s \in S}{\sTIreachable{s}} \subseteq I$.
% TODO: Make a note that this definition is different than the original, and
% reference the appendix where we include the proof that the two definitions
% are equivalent.
